Analyses

### 2021-05-27 report/figures/table_descriptives.tex
add labels to graphs of h's
add description analysis
rerun analyses

   <th style="text-align:left;"> name </th>

@@

   <td style="text-align:right;"> 33.80 </td>
   <td style="text-align:right;"> 16.34 </td>

@@

   <td style="text-align:right;"> 2.92 </td>

@@

   <td style="text-align:right;"> 2.27 </td>

@@

   <td style="text-align:right;"> 0.90 </td>

@@

   <td style="text-align:right;"> 3.35 </td>
   <td style="text-align:right;"> 2.62 </td>

@@

   <td style="text-align:right;"> 9.76 </td>
   <td style="text-align:right;"> 2.68 </td>

@@

   <td style="text-align:right;"> 1.28 </td>
   <td style="text-align:right;"> 0.54 </td>

@@

   <td style="text-align:right;"> 22.82 </td>
   <td style="text-align:right;"> 12.82 </td>

@@

   <td style="text-align:right;"> 5.91 </td>
   <td style="text-align:right;"> 2.03 </td>

@@

   <td style="text-align:right;"> 0.83 </td>

@@

   <td style="text-align:right;"> 4.48 </td>

@@

   <td style="text-align:right;"> 3.13 </td>

@@

   <td style="text-align:right;"> 2.06 </td>

@@

   <td style="text-align:right;"> 3.15 </td>

@@

@@

   <td style="text-align:right;"> 3.60 </td>

@@

   <td style="text-align:right;"> 3.26 </td>

@@

   <td style="text-align:right;"> 2.88 </td>

@@

   <td style="text-align:right;"> 5.85 </td>
   <td style="text-align:right;"> 1.78 </td>

>>>>

   <th style="text-align:left;"> Variables </th>

@@

   <td style="text-align:right;"> 33.64 </td>
   <td style="text-align:right;"> 16.37 </td>

@@

   <td style="text-align:right;"> 2.93 </td>

@@

   <td style="text-align:right;"> 2.28 </td>

@@

   <td style="text-align:right;"> 0.89 </td>

@@

   <td style="text-align:right;"> 3.36 </td>
   <td style="text-align:right;"> 2.67 </td>

@@

   <td style="text-align:right;"> 9.75 </td>
   <td style="text-align:right;"> 2.74 </td>

@@

   <td style="text-align:right;"> 1.27 </td>
   <td style="text-align:right;"> 0.53 </td>

@@

   <td style="text-align:right;"> 22.76 </td>
   <td style="text-align:right;"> 12.78 </td>

@@

   <td style="text-align:right;"> 5.88 </td>
   <td style="text-align:right;"> 2.04 </td>

@@

   <td style="text-align:right;"> 0.82 </td>

@@

   <td style="text-align:right;"> 4.46 </td>

@@

@@

   <td style="text-align:right;"> 3.94 </td>

@@

   <td style="text-align:right;"> 3.16 </td>

@@

   <td style="text-align:right;"> 2.87 </td>

@@

   <td style="text-align:right;"> 2.39 </td>
   <td style="text-align:right;"> 1.04 </td>

@@

   <td style="text-align:right;"> 2.74 </td>

@@

@@

   <td style="text-align:right;"> 5.86 </td>
   <td style="text-align:right;"> 1.77 </td>

### 2021-05-27 src/analysis/Analysis.Rmd
rerun analyses

```{r "check missings"}
descr <- d %>%
  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),2),
            `DV: Favorability` = round(sum(is.na(PT2))/n(),2),
            `DV: Representation` = round(sum(is.na(PT3))/n(),2),
            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),2),
            `Immigration (%)` = round(sum(is.na(PreT1))/n(),2),
            `Position: Immigration` = round(sum(is.na(PreT2))/n(),2),
            `Position: Defense` = round(sum(is.na(PreT3))/n(),2),
            `Position: Education` = round(sum(is.na(PreT4))/n(),2),
            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),2),
            `Ideology` = round(sum(is.na(PreT6))/n(),2),
            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),2),
            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),2),
            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),2),
            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),2),
            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),2),
            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),2),
            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),2),
            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),2),
            `Gender` = round(sum(is.na(F1))/n(),2),
            `Age` = round(sum(is.na(F2))/n(),2),
            `Region` = round(sum(is.na(F3))/n(),2),
            `Urbaness` = round(sum(is.na(F4))/n(),2),
            `Migration Background` = round(sum(is.na(F5))/n(),2),
            `Party Preference` = round(sum(is.na(F6))/n(),2),
            `Employment` = round(sum(is.na(F7))/n(),2),
            `Income` = round(sum(is.na(F8))/n(),2),
            `Education` = round(sum(is.na(F9))/n(),2)) %>%
  pivot_longer(cols = `DV: Trait Evaluation`:`Education`,
              names_to = "Variables", values_to = "% Missing Values") %>%
  filter(`% Missing Values` > 0)

@@

I recode the missing values of the variables `Urbaness`, `Party Preference`, `Employment`, and `Income` to the mean value of the respective variables -- median for `Party Precerence`.
For Income, I also include a dummy indicating whether the missing value was imputed.

```{r "add missings"}
means <- d %>%
  summarise(F4 = round(mean(F4, na.rm = T),0),
            F5 = round(mean(F5, na.rm = T), 0),
            F6 = max(names(table(F6))),
            F7 = round(mean(F7, na.rm = T),0),
            F8 = round(mean(F8, na.rm = T),0),
            F9 = round(mean(F9, na.rm = T),0))

d <- d %>%
  mutate(F4 = replace_na(F4, means$F4),
         F5 = replace_na(F5, means$F5),
         F6 = replace_na(F6, means$F6),
         F7 = replace_na(F7, means$F7),
         missing_F8 = if_else(is.na(F8), 1, 0),
         F8 = replace_na(F8, means$F8),
         F9 = replace_na(F9, means$F9))
rm(means, descr, scales)
```

@@

The figure below shows that the data is unbalanced for the variables: `Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`.
As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.

>>>>

```{r "check missings"}
descr <- d %>%
  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),4),
            `DV: Favorability` = round(sum(is.na(PT2))/n(),4),
            `DV: Representation` = round(sum(is.na(PT3))/n(),4),
            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),4),
            `Immigration (%)` = round(sum(is.na(PreT1))/n(),4),
            `Position: Immigration` = round(sum(is.na(PreT2))/n(),4),
            `Position: Defense` = round(sum(is.na(PreT3))/n(),4),
            `Position: Education` = round(sum(is.na(PreT4))/n(),4),
            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),4),
            `Ideology` = round(sum(is.na(PreT6))/n(),4),
            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),4),
            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),4),
            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),4),
            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),4),
            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),4),
            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),4),
            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),4),
            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),4),
            `Gender` = round(sum(is.na(F1))/n(),4),
            `Age` = round(sum(is.na(F2))/n(),4),
            `Region` = round(sum(is.na(F3))/n(),4),
            `Urbaness` = round(sum(is.na(F4))/n(),4),
            `Migration Background` = round(sum(is.na(F5))/n(),4),
            `Party Preference` = round(sum(is.na(F6))/n(),4),
            `Employment` = round(sum(is.na(F7))/n(),4),
            `Income` = round(sum(is.na(F8))/n(),4),
            `Education` = round(sum(is.na(F9))/n(),4)) %>%
  pivot_longer(cols = `DV: Trait Evaluation`:`Education`,
              names_to = "Variables", values_to = "% Missing Values") %>%
  filter(`% Missing Values` > 0)

@@

I recode the missing values of the variables `Urbaness`, `Migration Background`, `Income`, and `Education` to the mean value of the respective variables.

```{r "add missings"}
d <- d %>%
  mutate(F4 = replace_na(F4, round(mean(F4, na.rm = T),0)),
         F5 = replace_na(F5, round(mean(F5, na.rm = T),0)),
         F8 = replace_na(F8,round(mean(F8, na.rm = T),0)),
         F9 = replace_na(F9,round(mean(F9, na.rm = T),0)))
rm(descr, scales)
```

@@

The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`, and `Immigration (%)`.
As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.
